The functions associated with the poly-mod section are very powerful. They provide tools for non-linear modulation: cross-modulation of the two voice oscillators and modulation of the filter cut-off frequency by VCO B. 

A familiar and common synthesizer feature is that oscillators and/or filters (frequency, filter cut-off frequency, pulse width, etc.) are modulated by a \textit{low frequency oscillator (LFO)}. An LFO does not operate in the audible frequency range (it is "low frequency") and it has a fixed frequency which is independent from the note played. Poly-mod is different in that the modulation itself is in the audible range and the resulting non-linearity changes the frequency spectrum drastically. The resulting effect is comparable to FM synthesis known from digital FM synthesizers\footnote{FM synthesizers typically use phase modulation. However, the term \textit{FM synthesis} is commonly used for the family of synthesis methods or modulations in which an audio range signal is used to modulate the frequency control.}, although in the Prophet-600 it is more raw and fully analog. Like the oscillator sync function, cross-modulation is hardware implemented in the Prophet-600. To be precise, the Prophet-600 implements \textit{exponential} FM by feeding the audio signal directly into the voltage control of the oscillator.

The poly-mod control can be found in the poly-mod sub-panel. 

\begin{center}
\scalebox{0.4}{
  \begin{tikzpicture}[scale=0.8]

    \addpar{-18cm,3.5cm}{\envrouting \\ The routing options determine whether poly-mod is driven by the filter or the 2nd envelope};
    \draw[line width = 2pt, dashed] (-4cm,3.5cm) -- (1cm,3.5cm);


   \polymodesubpanel{0,0}
  \end{tikzpicture}
}
\end{center}

There are two modulation sources, \polymodenv and \polymodosc and two destinations, the pitch of oscillator A  and the filter cut-off frequency. Each source is activated using the respective panel switch, \polymodfreq and \polymodfilter. The \polymodosc determines how strongly the oscillator B modulates the poly-mod targets (destinations). It is instructive to consider the effect of oscillator B modulation on the two targets first and then explore the effect of envelope modulation.

\textbf{Cross-modulation}

\begin{itemize}
  \item When you set the \polymodfreq switch to \textit{on}, oscillator B modulates the frequency of oscillator A (frequency modulation, FM). Depending on the modulation strength the result is a wide and rich frequency spectrum of oscillator A which contains among others the sum and difference of multiples of the two oscillators frequencies. The spectrum strongly depends on the frequency difference and may be totally non-harmonic but also harmonic for carefully adjusted frequency settings. Typical spectra are often described as bell sounding. Note that in contrast to FM synthesizers which use highly accurate sin waves, the oscillator output of the Prophet-600 does not have the same basic accuracy and the available waveforms already contain higher harmonics (triangle, sawtooth, etc.). Therefore the FM result in the Prophet-600 is typically more drastic and dirtier and requires classic subtractive methods for shaping the sound, i.e. the application of the low pass filter. Another important difference to FM synthesizers is that the Prophet-600 (like most analog poly synthesizers with cross-modulation capability) uses exponential FM. It is characteristic of this feature that the modulation strength changes the pitch of the sound. Unless you are using this for experimental purposes and in case your intention is to obtain a harmonic sound to be play polyphonically, you should treat \polymodosc as a static and carefully adjusted parameter.
  \item When you set the \polymodfilter switch to \textit{on}, oscillator B modulates the filter cut-off frequency of the low pass filter. Like oscillator FM this is a non-linear modulation. This effect can also produce a wide frequency spectrum which may or may not be harmonic, depending on the relative frequency of oscillators A and B. The effect is more pronounced at low filter cut-off frequencies. The resonance also has a strong influence on the effect.  
\end{itemize}

Note that unless you use oscillator sync at the same time, poly-mod is very pitch sensitive so that patches which use strong poly-mod may need to be fine tuned using \freqfine. Also, poly-mod patches may sound off on a cold unit due to temperature dependent drift and generally it maybe necessary to retune the synth more often when using extreme poly-mod patches. You should be aware that the harmonic integrity of a patch may vary from instrument to instrument and - more importantly - that there can be voice-to-voice differences. Therefore medium to strong poly-mod patches that sound good on one instrument may not immediately sound good on another unit or may even not be fully reproducible. In most cases you can compensate by adjusting \freqfine, \polymodosc or even \oscfreq (better A than B) if everything else fails. However, you may find that in your unit the differences among the voices are so strong that beyond a certain poly-mod strength, patches start sounding detuned (in polyphonic play). The main reasons for such behaviour are related to oscillator chip specific variations as listed below. When you use oscillator sync, pitch related problems of poly-mod are not an issue, so the following information is relevant when you don't use sync.

\begin{itemize}
  \item \textit{Differences in pulse width}: The pulse width is generally different for all chips (within specification ranges). For the timbre of sound such variations do not matter much (unless you are toying with the break-up points on either side). However, pulse width leads to a DC voltage component (i.e. the voltage of the waveform spends more time either below or above zero) and since in cross-modulation the signal is fed into the oscillator voltage control with no DC removal mechanism in place, this directly produces a shift in frequency, i.e. when you use cross-modulation with the pulse waveform on oscillator B active, the pulse width translates directly into a pitch shift of oscillator A. You may compensate for this by fine tuning (see above), but since pulse width is not precisely normalized among the voices, you may find that these differences lead to voice-to-voice detuning. If that is the case in your instrument, you should avoid using the pulse waveform on oscillator B for medium to strong poly-mod patches.      
  \item \textit{Differences in scaling}: The scaling differences in the oscillators also have an impact on cross-modulation, because these are effectively differences in voltage to frequency relations. If you find that your voices tend to have a strong variation in poly-mod response, you may be able to reduce the effect but careful scaling adjustment.
  \item \textit{Differences in DC offset}: There can be inherent, chip specific differences in the DC offset of output waveforms. This is more likely in the sawtooth and pulse width wave forms. In this case you may try to avoid sawtooth waveforms on oscillator B for medium to strong poly-mod patches.
\end{itemize}

Please refer to the technical excursion at the end of the section for more background on the design implications of the poly-mod implementation in the Prophet-600. In order to assess the voice-to-voice differences in poly-mod response, you can use the following method. Create a strong poly-mod patch and calibrate it to be harmonic (i.e. no beating sounds) using one note (voice). Make sure to choose a high sustain and short release. You can then start from key C and play and hold 6 notes up the scale. Each note is assigned to a different voice. When you release all but one note you will hear only that one voice. Check if there is a beating sound. You can either assess the level detuning by listening or "measure" it by adjusting the frequency of oscillator A to remove the beating. If you choose the \assign option \textit{first} (see section \ref{poly-unison-voice}) and use zero release (filter and amplitude), the relation of note to voice will be completely reproducible. Activating and deactivating voices one-by-one (see \ref{voices}) is also possible (but more cumbersome).

\textbf{Envelope pitch modulation}

The second poly-mod modulation source is the poly-mod envelope. When the \polymodfreq switch is \textit{on}, the envelope modulates the pitch of oscillator A at the strength set by the \polymodenv dial. The \polymodenv control is bipolar. It  provides negative (inverse modulation, lowering the pitch) and positive modulation (raising the pitch). The pitch shift is harmonic and in the sustain phase of the envelope the maximum obtainable pitch shift (i.e. maximum positive or negative value of \polymodenv and sustain at full value) corresponds to $\pm 30$ semitones.

Note that the poly-mod envelope only affects the frequency of oscillator A (and never the filter cut-off frequency) even if the second destination, the \polymodfilter switch, is also \textit{on}. The filter cut-off frequency is already modulated by the filter envelope. Depending on the menu parameter \envrouting the source envelope is either the filter envelope or the 2nd envelope, see below for details on the options.

Pitch modulation by envelope is not actually a cross-modulation function. However, the association with poly-mod is useful because of the strong effect pitch (difference) has on cross-modulation. What can it be used for? Envelope modulation is a form of time modulation. It can change the sound from attack through hold to release. By time modulating the pitch in combination with cross-modulation (and/or sync), the sound can be made to sweep through different spectra, ranging from apocalyptic noise through bell sounds to delicate transients. The way humans perceive natural sounds is strongly influenced by the frequency characteristics of the transients (typically short lived high frequency components) in the attack and decay phases of the sound. This is best modelled using an envelope. So, being able to modulate the composition of frequency spectrum by envelope is a versatile tool for advanced sound design. This was probably the original thought behind putting the \polymodenv control in the poly-mod section.

In order to further expand the sound design possibilities, the latest firmware upgrade offers an envelope routing option, which is inspired by a similar setup in the Roland JX8P synthesizer. Having different envelopes modulating the filter and the poly-mod opens up new possibilities in the sound and spectrum dynamics. The following section explains the routing options. 

The menu parameter \envrouting determines if the filter envelope or the 2nd envelope is used in poly-mod\footnote{Up to version 2.1 RC3 the filter envelope was "hard wired" to poly-mod.}.

\begin{itemize}
  \setlength\itemsep{0cm}
  \item \textit{standard}: In this "standard" routing the amplitude is modulated by the 2nd envelope and the poly-mod is modulated by the filter envelope. This is the setup of the original Prophet-600 and versions 2.0 and 2.1 RC3. It is also the default in \version.
  \item \textit{poly-amplitude}: In this routing both the amplitude and the poly-mod are modulated by the 2nd envelope. 
  \item \textit{poly}: In this routing the amplitude is modulated by the filter envelope and the poly-mod is modulated exclusively by the 2nd envelope. Therefore the poly-mod time modulation is completely free, at the expense of having filter modulation and amplitude tied together.
  \item \textit{gate}: In this routing the amplitude is not modulated at all, but behaves like a gate (similar to electronic organs). The poly-mod is modulated exclusively by the assignable envelope. Therefore the poly-mod modulation is completely free at the expense of a less dynamic sound evolution.
\end{itemize}  

\scalebox{0.4}{
  \begin{tikzpicture}[scale=0.8]
   \envroute{0,0}
  \end{tikzpicture}
}

\textbf{Oscillator sync and poly-mod}

As explained in section \ref{osc}, you can sync oscillator A to oscillator B using the \oscsync switch in the sub-panel for oscillator B. This can also be view as a variant of cross-modulation. The sync function can also be combined with frequency modulation as described above. 

Combining oscillator sync with poly-mod pitch modulation by envelope can be used to produce interesting short transients or slow sound evolutions. For example, when oscillator A is a pulse wave, then sync'ing this wave to oscillator B and time modulating the pitch of oscillator A has the effect of pulse width modulation by envelope. It creates a change in timbre which can be short to simulate plucking an brassy attacks or long to produce a sweep of the sound spectrum.

\textbf{Starting points for patch design with poly-mod and sync}

Using poly-mod in combination with oscillator sync, different modulations strengths for different oscillator pitches with different filter and modulation shapes - this offers a very wide field of experimentation. Here are two prototypical starting points:

\begin{itemize}
  \item Set the envelope routing to \textit{standard}, tune both oscillators to the same frequency. In the poly-mod section turn source VCO B to zero and deactivate the filter modulation. Then set VCO A to sync and switch on the poly-mod target frequency oscillator A. Experiment with the poly-mod envelope source amount, oscillator A frequency and filter envelope attack and decay. This produces an evolving sync sound which, for high envelope amounts, can be tuned to a very assertive synth solo sound.
  \item Set the envelope routing to \textit{standard}, tune both oscillators to the same frequency. In the poly-mod section turn the poly-mod envelope source amount to zero, deactivate the filter modulation  and switch on the poly-mod target frequency oscillator A. Switch off VCO A sync. Now experiment with the poly-mod envelope source amount and oscillator B fine tune. Either you enjoy the drastic spectra you will get for most of the settings or you carefully adjust the frequencies to find the sweet spots at which the spectrum clears. This is the typical way to produce very rich and brassy timbres but normally this also needs some filter cut-off to softly cut away the highest frequencies. For stronger poly-mod, oscillator B fine tune may not be sufficient and it may be necessary to also adjust the frequency of oscillator A. For this it is useful to set the granularity of the frequency dials to free/octave (i.e. oscillator A free and oscillator B octave). Notice that other controls also influence the pitch, such as the oscillator B wave selection and pulse width (see description of bleed bug below) so that you may find that you need to compensate for this effect with fine tuning.   
\end{itemize} 

\textbf{Technical excursion 1: pulse width bleed bug}

The firmware versions 2.0 and 2.1 RC3 contain a software error which incorrectly resets the pulse widths of oscillators A and B. This manifests itself under the following conditions: \polymodosc is turned up and the poly-mod target \polymodfreq is active. The wave shape pulse of oscillator B is not activated. In this case the incorrect reset of the pulse widths leads to a wrong frequency in oscillator A. The effect becomes stronger with higher settings of \polymodosc. In version \version this bug is corrected but in order to ensure backwards compatibility of older patches, the bug is automatically switched on when loading such patches to faithfully reproduce the behaviour of prior firmware versions.  The bug toggle is the \syncbug which can be set to \textit{off} and \textit{on}. The default value (default patch) is \textit{off}.

\textbf{Technical excursion 2: vulnerable exponential FM in the Prophet-600}

The Prophet-600 has a hardware design flaw which leads to a bleed of the DC component of the oscillator B output to the pitch of oscillator A when \polymodosc with destination \polymodfreq is active. While the CEM3340 oscillator chip has a dedicated support for linear frequency modulation, Sequential Circuits chose no to use that option but instead designed the circuitry such that the output of oscillator A is fed directly into the control voltage of oscillator A. The control voltage input (i.e. the input that determines the frequency of oscillator A) is the sum of the note related voltage (i.e. the note that the oscillator is supposed to play) and the output of oscillator B. The amount of oscillator B contribution is set by \polymodosc. This is effectively exponential FM: the frequency doubles with each 1V of control voltage input. Exponential FM is common in polyphonic synthesizers and you find the same basic mechanism in the Prophet-5, for example. Exponential FM has the disadvantage that it changes the pitch. Since we are dealing with non-calibrated, CV controlled components here, this leads to potential differences between different units as far as the amount of poly-mod is concerned. Medium to strong poly-mod patch may not be fully portable from one unit to another, as a result. There is another problem in the Prophet-600 design, however. The DC component of oscillator B output is not removed before being fed into oscillator A. For using the linear FM input, the CEM3340 specification recommends using a capacitor to remove low frequency components. No such mechanism is in place in the Prophet-600 exponential FM. As a result any DC voltage component from oscillator B directly changes the basic frequency of oscillator A. While you may accept the general effect that \polymodosc changes the pitch, the presence of the DC voltage has the distinctive disadvantage that chip specific (and therefore voice specific) variations affect the pitch. In the worst case, poly-mod completely detunes the Prophet-600. 

There are three main sources for poly-mod induced voice variations. First, away from the pulse width mid-position pulse waveforms have a DC component and therefore oscillator B pulse width creates a shift in oscillator A frequency. Since pulse width is chip specific (i.e. with variations within production specifications) each voice can produce a different oscillator B pitch depending on the pulse width variation of oscillator A. Second, the waveform output can have a chip specific DC voltage level. This affects also the sawtooth waveform (which has a non-zero DC component to start with). Third, while the chip specific relation of voltage to frequency is compensated for by the built-in tuning mechanism, the FM voltage input is not corrected for this and as a result, the DC offsets from the voices (even if identical) lead to different voltage shifts depending on the different scaling characteristics. 

The bottom line is that instrument specific voice-to-voice variations may mean that you have difficulties to use strong poly-mod harmonically. Patches that sound clear and rich on another instrument may sound detuned and bad and corrections which affect all voices are not sufficient to clear the harmonics. The only options are to take care of scaling adjustments or to try to replace selected CEM3340 chips (hopefully the information here helps you to determine which chip should be replaced). For your own patches it is recommended to avoid pulse (and then probably also sawtooth) waveforms on oscillator B for poly-mod.    

A future version of the upgraded firmware may contain a calibration and correction mechanism in order to compensate for chip specific differences not only for pitch but also for poly-mod. Popular Prophet-600 hardware modifications include inserting a capacitor into the poly-mod circuitry in order to the remove the DC offset of oscillator B. This change makes the instrument much more consistent but it also alters the characteristics significantly. 
