\textbf{Power Switch}

When turned on, the Prophet-600 starts in normal mode if no buttons are held down. The Prophet-600 can be powered up in two different modes related to maintenance tasks: firmware upgrade mode (see section \ref{fwupgrade}) and scaling adjustment mode (see section \ref{scalingadj}).  

When you start the instrument in normal mode the specification of the installed version is scrolled through the display. After power-up the instrument remembers that last state. It will starts in \livemode or \presetmode and in \presetmode it activates and loads the last selected patch.

Note: earlier versions of the firmware upgrade went into tuning mode directly when powered up. From version 2.1 RC3 on this is no longer the case. In practice, the instrument needs to warm up and stabilize before tuning makes sense. For details on tuning see section \ref{tuning}. If the tuning data is invalid or there is no tuning data (for example after a firmware upgrade using USB), the Prophet-600 goes into tuning mode on start-up.

\textbf{Line voltage selector}

The selector next to the main plug provides the option to switch between 110V and 220V mains voltage, whichever is appropriate for the line voltage where the instrument is operated. Use a flat head screw driver to rotate the line voltage selector to the appropriate setting. Instrument should be powered down and unplugged when line voltage selector is adjusted.

\textbf{Fuse holder}

Fit the fuse according to the selected line voltage, i.e. 110V 1/2A, slo-blo, 220V 1/4A slo-blo.

\textbf{Audio out / headphone jack}

To drive a preamp or an amp, a standard monophonic cable can be used. Or if there are two audio destinations (e.g. one to remain “dry” while the other is processed), a stereo cable may be more convenient.

The Prophet-600 has a monophonic output signal, but the jack is wired so that both sides of standard stereo headphones can be driven. The headphones have a minimum impedance of 1200 Ohms per element (600 Ohms in parallel).

\textbf{Filter CV In}

This jack accepts a 0-10 V control voltage (CV) which is applied to the filter cut-off frequency (all voices). This enables remote and spontaneous increase (but not decrease) of the filter cut-off making the sound brighter. The CV can be usually provided by an accessory voltage pedal or an external LFO. The strength of the external CV influence is controlled by an additional patch parameter (see section \ref{extcv}). The default value (cf. default patch) of this parameter is zero. 

Note that popular "noise mods" for the Prophet-600 use the external CV In control as an auxiliary control voltage for the noise amount. For such modifications the patch parameter controls the noise level.

\textbf{Foot switch}

The foot switch jack allows for the use of a sustain pedal (only supported from version 2.1 RC3 onwards). The pedal should be contact open at rest.

\textbf{Cassette In/Out (disabled with GliGli mod)}

\cassettein can be used for sending a pulsed clock to the Prophet-600 to sync to the sequencer and/or arpeggiator. However, in the upgraded version the functionality to receive or send patch data via \cassettein has been omitted. 

When you set the instrument to use external analog clock (using the setting \clocksync), the \datadial (when set to control \clock) selects the clock divider rather than a clock speed. See section \ref{sync} for details.

\textbf{MIDI In/Out}

The Prophet-600 is equipped with standard MIDI In and MIDI Out connections. The MIDI receive and send channels can be configured in the miscellaneous settings, see section \ref{midiintegration} on MIDI integration.  
